Phenology and Mycorrhizae Manuscript

### 2023-02-10 manuscriptCode_phenologyAndMycorrhizae.Rmd
Fit LRs to ERA data and used to gap fill temp and precip

for(f in seq_along(funTypes)){
  calculateDailyWeather(dataName=dataName,dataPath=dataPath,varName=varName,funType=funTypes[f],funName=funNames[f])
  #Calculate LRs
  # gapFillFromDayMet_verticalProfiles(dataName=dataName,dataPath=dataPath,varName=varName,funName=funName)
} #****Need to rerun

@@

##NEON Precipitation
```{r,eval=FALSE}
dataName="NEON_PrecipitationData"
NEON_ID='DP1.00006.001'
selectColumns <- c('precipBulk','precipExpUncert','precipQF')
inFileName <- c("PRIPRE_30min.csv","SECPRE_30min.csv")
varName <- "precipBulk"
if(downloadData){
  downloadNEONdata(dataName=dataName,NEON_ID=NEON_ID)
}
combineNEONdata(dataName=dataName,NEON_ID=NEON_ID,selectColumns=selectColumns,
                inFileName=inFileName,dataPath=dataPath)
calculateDailyWeather(dataName=dataName,dataPath=dataPath,varName=varName,funType=sum)

#gapFillFromDaymet(dataName=dataName,dataPath=dataPath,varName=varName)

>>>>

for(f in seq_along(funTypes)){
  calculateDailyWeather(dataName=dataName,dataPath=dataPath,varName=varName,funName=funNames[f])
  gapFillFromERA_verticalProfiles(dataName=dataName,dataPath=dataPath,varName=varName,funName=funName)
}

@@

##NEON Precipitation
```{r,eval=FALSE}
dataName="NEON_PrecipitationData"
NEON_ID='DP1.00006.001'
selectColumns <- c('precipBulk','precipExpUncert','precipQF')
inFileName <- c("PRIPRE_30min.csv","SECPRE_30min.csv")
varName <- "precipBulk"
if(downloadData){
  downloadNEONdata(dataName=dataName,NEON_ID=NEON_ID)
}
combineNEONdata(dataName=dataName,NEON_ID=NEON_ID,selectColumns=selectColumns,
                inFileName=inFileName,dataPath=dataPath)
calculateDailyWeather(dataName=dataName,dataPath=dataPath,varName=varName,funName="sum")

gapFillFromERA_verticalProfiles(dataName=dataName,dataPath=dataPath,varName=varName,funName="sum")
